### 2019-02-14 2-Chapters/5-Chapter/ALT_2018__MPBandits.git/mpBandits_appendix.tex
Typo

\begin{figure}[!h]
    \centering
    % \begin{subfigure}[!h]{0.85\textwidth}
        \includegraphics[width=1.00\textwidth]{MP__K9_M3_T123456_N100__8_algos/all_RegretCentralized____env1-1_7803645526012310577.pdf}
    % \end{subfigure}
    % ~
    % \begin{subfigure}[!h]{0.85\textwidth}
        \includegraphics[width=1.00\textwidth]{MP__K9_M3_T123456_N100__8_algos/all_RegretCentralized_semilogy____env1-1_7803645526012310577.pdf}
    % \end{subfigure}
    \caption[Regret for $M=3$ players for $K=9$ arms, horizon $T=123456$, for $100$ repetitions on problem $\mu=[0.1,\dots,0.9]$]{Regret (in log-$y$ scale on the right) for $M=3$ players for $K=9$ arms, horizon $T=123456$, for $100$ repetitions on problem $\mu=[0.1,\dots,0.9]$. With a perfect knowledge on the gap ($\Delta=0.1$ here) and by using the parameters suggested from their respective articles, \MEGA{} and \MusicalChair{} perform badly in this simple setting, even with the knowledge of the horizon $T$ for \MusicalChair{}. The first two \MusicalChair{} instances use the optimal $T_0$ value from \cite{Rosenski16}, with $\varepsilon$ taken slightly smaller than the gap $\Delta$ ($\varepsilon=0.99 \Delta$), and respectively with $\delta=0.5$ and $\delta=0.1$, for which the regret can bounded with probability $0.5$ and $0.9$ respectively. The third instance uses the optimal $T_0$ corresponding to $\delta=1/T$, that is guaranteed to have an expected regret of order $\log(T)$.}
    \label{fig:5:MP__K9_M3_T123456_N100__8_algos}
\end{figure}

>>>>

\begin{figure}[!h]
    \centering
    % \begin{subfigure}[!h]{0.85\textwidth}
        \includegraphics[width=1.00\textwidth]{MP__K9_M3_T123456_N100__8_algos/all_RegretCentralized____env1-1_7803645526012310577.pdf}
    % \end{subfigure}
    % ~
    % \begin{subfigure}[!h]{0.85\textwidth}
        \includegraphics[width=1.00\textwidth]{MP__K9_M3_T123456_N100__8_algos/all_RegretCentralized_semilogy____env1-1_7803645526012310577.pdf}
    % \end{subfigure}
    \caption[Regret for $M=3$ players for $K=9$ arms, horizon $T=123456$, for $100$ repetitions on a fixed problem]{Regret (in log-$y$ scale on the right) for $M=3$ players for $K=9$ arms, horizon $T=123456$, for $100$ repetitions on problem $\mu=[0.1,\dots,0.9]$. With a perfect knowledge on the gap ($\Delta=0.1$ here) and by using the parameters suggested from their respective articles, \MEGA{} and \MusicalChair{} perform badly in this simple setting, even with the knowledge of the horizon $T$ for \MusicalChair{}. The first two \MusicalChair{} instances use the optimal $T_0$ value from \cite{Rosenski16}, with $\varepsilon$ taken slightly smaller than the gap $\Delta$ ($\varepsilon=0.99 \Delta$), and respectively with $\delta=0.5$ and $\delta=0.1$, for which the regret can bounded with probability $0.5$ and $0.9$ respectively. The third instance uses the optimal $T_0$ corresponding to $\delta=1/T$, that is guaranteed to have an expected regret of order $\log(T)$.}
    \label{fig:5:MP__K9_M3_T123456_N100__8_algos}
\end{figure}
